\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{Problem Statement and Goals: Physics Game - Collisions and Gravity}
\author{} % Add author name here
\date{} % Add date here

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
% Add revision history here
\bottomrule
\end{tabularx}
\end{table}

\section{Problem Statement}
Develop a physics-based gaming application focusing on realistic collision dynamics and gravitational interactions. The goal is to create an engaging gameplay experience emphasizing the application of physics principles.

\subsection{Problem}
% Elaborate on the specific problem your game is solving

\subsection{Inputs and Outputs}
% Define the high-level inputs and outputs of the game

\subsection{Stakeholders}
% List and describe the stakeholders of this project

\subsection{Environment}
% Describe the hardware and software environment

\section{Goals}
% List down the specific goals of the project

\section{Game Elements}
\begin{itemize}
    \item Projectile: Object with initial position, velocity, and mass.
    \item Targets/Obstacles: Multiple targets or obstacles with varying shapes and sizes.
\end{itemize}

\section{Physics Simulation}
\begin{itemize}
    \item Realistic collision interactions.
    \item Gravity influence on projectile trajectory.
    \item Optional additional forces like wind.
    \item Visual feedback for collisions.
\end{itemize}

\section{Controls}
\begin{itemize}
    \item Intuitive user interactions.
    \item Adjustable launch angle, force, and other parameters.
\end{itemize}

\section{Graphics and Sound}
\begin{itemize}
    \item Enhanced graphics for visual appeal.
    \item Complementary sound effects.
\end{itemize}

\section{Stretch Goals}
% Define any additional goals that go beyond the initial scope

\end{document}
